%-------------------------
% Resume in LaTeX - ATS Optimized
% Optimized for: AI/ML Engineering Internship in Industry
% Author : Muhammed Yıldız
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge\scshape Muhammed Yıldız} \\ \vspace{2pt}
    \small
    \href{mailto:mhmmdyildiz@proton.me}{\underline{mhmmdyildiz@proton.me}} $|$ 
    \href{https://linkedin.com/in/myzz}{\underline{linkedin.com/in/myzz}} $|$
    \href{https://github.com/myz21}{\underline{github.com/myz21}} $|$
    \href{tel:+905551926713}{+90 555 192 6713}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Summary}
    \small{\textbf{AI Researcher} and Computer Engineering undergraduate skilled in \textbf{NLP, computer vision, and generative AI}. Proven ability to train deep learning models and \textbf{deploy AI web services}. Recognized \textbf{hackathon winner} and technical event organizer}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ankara Yildirim Beyazit University}{Ankara, Turkey}
      {B.Sc. in Computer Engineering; GPA: 3.24/4.0}{Oct. 2023 -- June 2027 (Expected)}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hacettepe Biological Data Science Lab}{Aug. 2025 -- Present}
      {Undergraduate Researcher}{Ankara, Turkey}
\vspace{0.5pt}
      \resumeItemListStart
\resumeItem{Developed \textbf{ProtMamba}, a \textbf{State-Space Model} for generative protein language modeling, bypassing Transformer quadratic bottlenecks for linear-time inference.}
\resumeItem{Engineered scalable \textbf{PyTorch} data pipelines for 60M+ sequences, utilizing \textbf{Hugging Face} for tokenization and dynamically tracking large-scale training/hyperparameter optimization experiments via \textbf{Weights \& Biases (W\&B)}.}

      \resumeItemListEnd
\vspace{5pt}
    \resumeSubheading
      {Nanominds}{July 2025 - August 2025}
      {Intern}{İstanbul, Turkey}
\vspace{0.5pt}
\resumeItemListStart
\resumeItem{Researched \textbf{AI workflows in Venture Capital} and analyzed AI use cases across the investment process. I also studied \textbf{Hybrid RAG}, focusing on combining \textbf{dense} and \textbf{sparse retrieval} for improved knowledge systems. The results were presented as a strategic report to the venture capital firm.}

      \resumeItemListEnd
\vspace{5pt}
    \resumeSubheading
      {Zenith AI Team}{March 2025 -- Present}
      {Team Lead \& Computer Vision Engineer}{Ankara, Turkey}
\vspace{0.5pt}
      \resumeItemListStart
        \resumeItem{Engineered a vision-based navigation system for a GPS-denied UAV challenge (TEKNOFEST), securing \textbf{finalist} status with the \textbf{highest semi-final trajectory score (0.894)} via \textbf{ORB odometry}; optimized \textbf{YOLO} models via \textbf{data augmentation} to robustly detect objects from challenging aerial imagery.}
        
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Technical Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{nanoGPT} $:$ \emph{\textbf{Pytorch/Numpy}} \href{https://github.com/myz21/GPT}{(Click for project - GitHub)}}{Jan. 2026}
          \resumeItemListStart
            \resumeItem{Built a \textbf{GPT language model from scratch} using decoder-only transformer architecture with character-level tokenization, trained for 50 epochs on RTX A5000 GPU over 53 hours to generate contextual text descriptions.}
          \resumeItemListEnd
    \vspace{0.1pt}

      \resumeProjectHeading
          {\textbf{DoctorGPT: Medical Assistant} \href{https://github.com/myz21/DoctorGPT}{(Click for project - GitHub)}}{July 2025}
          \resumeItemListStart
            \resumeItem{Engineered an intelligent conversational AI web service utilizing \textbf{LangChain, Gemini, FastAPI, and Pydantic} to deliver highly responsive, context-aware, and structured natural language interactions for users. }
          \resumeItemListEnd
\vspace{0.1pt}


      \resumeProjectHeading
          {\textbf{E-Corp Customer Insight Analysis} $|$ \emph{\href{https://lnkd.in/dAXxunMu}{2nd Place - Click for post} }}{Mar. 2025}
          \resumeItemListStart
            \resumeItem{Awarded \textbf{2nd Place} by achieving \textbf{0.92 R-squared score} in revenue prediction via optimized \textbf{AdaBoost} and extensive EDA using \textbf{Pandas} and \textbf{Matplotlib}.}
          \resumeItemListEnd
\vspace{0.1pt}

      
    \resumeProjectHeading
        {\textbf{The Traitor — Client/Server Game (C++/SFML)} \href{https://github.com/M-Enes/OOP_Group19}{(Click for project - GitHub)}}{Dec. 2025}
        \resumeItemListStart
          \resumeItem{Built SFML client UI (menu/lobby/action), avatar selection/rendering, and game-over/win screens.}
          \resumeItem{Integrated with \textbf{TCP client--server networking} and \textbf{packet-based messaging} for multiplayer gameplay.}
        \resumeItemListEnd
        
    \resumeSubHeadingListEnd

%-----------LEADERSHIP & AWARDS-----------
\section{Leadership \& Awards}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Vodafone AI Ideathon (Bi' Düşünsene)} $|$ \href{https://lnkd.in/dZVzU3Wx}{\textbf{3rd Place Winner - Click for post}}}{Dec. 2024}
      \resumeItemListStart
        \resumeItem{Conceptualized an early Earthquake Warning System integrated into the Vodafone ecosystem, leveraging Fiber Optic Sensing technology to detect seismic vibrations via existing telecommunication infrastructure.}
      \resumeItemListEnd

    \vspace{4pt}



    \resumeProjectHeading
      {\textbf{Happy Hacking Space Code Jam} $|$ \href{https://www.linkedin.com/posts/myzz_dear-connections-i-finished-the-code-jam-activity-7290399937270308865-ghH9/}{\textbf{2nd Place Winner - Click for post}}}{Jan. 2025}
      \resumeItemListStart
\vspace{0.2pt}
        \resumeItem{Ranked 2nd among competitors by solving complex algorithmic challenges under strict time constraints.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI/ML Frameworks}{: PyTorch, TensorFlow, Scikit-learn, LangChain, HuggingFace, OpenCV, YOLO} \\
     \textbf{Tools \& DevOps}{: Git, Docker, FastAPI, Streamlit, Pandas, NumPy, Matplotlib, Linux} \\
     \textbf{Languages}{: Python, C++, Java, SQL}
    }}
 \end{itemize}

\end{document}